---
title: "Ex7- Descriptive Statistics in R"
author: "Amal Sujith"
date: "30/09/2021"
output: html_document
---

## Amal Sujith

```{r}
library(MASS)
head(survey)
data("survey")
df <-survey
df <- na.omit(df)
str(df)
```




###1.How many the left and right handers are there?

```{r}
handers <- table(df$W.Hnd)
handers

```


### 2.Find the relative frequency distribution of left and right handers and display them with the precision of two decimal places.
```{r}
sample_size=nrow(df)
old=options(digits=2) #two decimal places
rel_freq=handers/sample_size
rel_freq
```


### 3.Display the male left hander and female left hander in the column format.

```{r}
library(dplyr)
```

```{r}
res <-df %>%
  filter(W.Hnd=="Left") %>%
  select(Sex)
cbind(res)
```

### 4.What percentage of male right handers never smokes?
```{r}
n_total <- nrow(survey)

tot <- df %>%
  filter(Sex=='Male', W.Hnd=='Right', Smoke=='Never')

n <- nrow(tot)
male_nosmoke = (n/n_total)*100
male_nosmoke

```


### 5.	Find the range of students’ height participated in the survey.
```{r}
height=df$Height
height_range = range(height) 
height_range
```

### 6.Break the height range into non-overlapping sub-intervals by defining a sequence of equal distance break points of 10 by rounding the range to nearest integer.

```{r}
breaks=seq(152,201,by=10)
stud_h=df$Height
h_cut=cut(stud_h,breaks,right=FALSE) 
h_cut

```

```{r}
#bins have been created
h_freq=table(h_cut)
h_freq
```

### 7	Find the distribution of the height range according to the sub-intervals with cut with its right boundary opened. Display it in column form.
```{r}
breaks=seq(152,201,by=10)
stud_h=df$Height
h_cut=cut(stud_h,breaks,right=FALSE) 
h_cut
```


```{r}
#bins have been created
h_freq=table(h_cut)
h_freq

```

```{r}
cbind(h_freq)

```


###8.	Which height range of students has mostly participated in the survey?
```{r}
which.max(h_freq)

```


###9.	Compute the mean, variance and standard deviation of the height of the students participated in the survey.
```{r}
height_range = df$Height

mn_height = mean(height_range)
mn_height 

var_height=var(height_range)
var_height

std_height= sd(height_range)
std_height
```




### 10.	Which category of clap students has the maximum writing hand span? 
```{r}
res <- df%>%
  group_by(Clap)%>%
  summarize(mx=max(Wr.Hnd))
  res[which.max(maxClap$mx),]["Clap"]
  head(1)
res
```



### 11.	Compute the covariance and correlation between height and writing span.
```{r}
height=df$Height
writing_span=df$Wr.Hnd
#Covariance
cov(height,writing_span)

#Correlation
cor(height,writing_span)
```





###. 12.	Display the 30%, 60% and 80% percentile of the height data.

```{r}
percentile_height=quantile(df$Height,c(.30,.60,.80))
percentile_height

```



#### Frame any three questions on descriptive statistics to analyse the categorical & quantitative variables present in the data of your choice.

```{r}
data <- read.table("50_Startups.csv",header=TRUE,sep=",")
head(data)
```

### 13.	Find the range difference of Profits of the startups and also find the innter quantrile range

```{r}
profit=data$Profit
rangediff=max(profit)-min(profit)
rangediff
```

```{r}
Inner_Range_profit=IQR(profit)
Inner_Range_profit
```

```{r}
par(mar=c(2,2,2,2))
boxplot(profit,horizontal=TRUE)
```

### 14.Show the linear dependecy between Profit and Research and Development Expenditure

```{r}
re <- data$R.D.Spend
profit.lm <- lm(profit ~ re , data=data)
resid <- rstandard(profit.lm)

par("mar")

par(mar=c(1,1,1,1))
qqnorm(resid,main='Profit',xlab="normal score",ylab="std. residuals")
qqline(resid)
```



### 15.Find the moment , skewness and kurtosis of Marketing.Spend

```{r}
library(e1071)



```

```{r}
re <- data$Marketing.Spend 
moment(re,order=3, center=TRUE)
```

```{r}
skewness(re)
```

```{r}
kurtosis(re)
```

