---
title: "ex9"
author: "Zeel1229"
date: "21/10/2021"
output: html_document
---

## Name: Desai Zeel Amitkumar
## Registration No: 19BCE1229

```{r}
cancer <- read.csv("C:/Users/desai/OneDrive/Desktop/dfa/lab/lab9/diabetes.csv")


#dimension of the data
dim(cancer)

#structure of the data
str(cancer)


#view of the data in a table
View(cancer)


#fetching top 6 rows
head(cancer)

#fetching last 6 rows
tail(cancer)

#summary of the data
summary(cancer)

############       Cleaning data   #################
#checking for missing values in the data
any(is.na(cancer))  #NA NaN


#checking for the total no. of missing values in the data
sum(is.na(cancer))

```


```{r}

cancer_unclean <- cancer
newcancer <- na.omit(cancer_unclean)
```

```{r}
any(is.na(cancer)) 
```

```{r}
sum(is.na(cancer))
```



```{r}
library(MASS)

```

```{r}
library(dplyr)
```

```{r}
library(tidyverse)
```

##Display random 3 values under each category of pregnancies.

```{r}
newcancer %>% 
  group_by(Pregnancies) 
  slice_sample(newcancer, n=3)
```

##### Arrange all patients whose glucose=109 and Insulin =0 ccording to descending order of their age.

```{r}
newcancer %>%
  filter(Glucose =="109",Insulin =="0")%>%
  arrange(desc(Age))
```

### 	Find the minimum SkinThickness of diabetic and non diabetic patients.


```{r}
newcancer %>%
 
  group_by(Outcome) %>%
  summarize(SkinThickness=min(Outcome))
```


#Infernce
##0=diabetic 1-non-diabetic



#Show the frequency distribution graphically by bar chart

```{r}
library(ggplot2)
```

```{r}
c_factor <- factor(newcancer$Outcome,levels = c("0","1"),labels = c("Non-diabetic","Diabetic"))
ggplot(newcancer,aes(x=c_factor))+geom_bar()+labs(title = "Frequency distribution graphically",x='Cancer class',y='Frequency')
```

#### 5.Draw the histogram of age distribution with the title as ‘Age distribution’ and xlabel as ‘Age range’ and ylabel as ‘frequency’..

```{r}
hist(newcancer$Age ,main = "Age Distribution", xlab= "Age Range", ylab ="frequency")
```

### 6. Reveal the relationship between the age and Outcome using scatter plot.

```{r}
plot(newcancer$Age,newcancer$Outcome)
```

```{r}
ggplot(newcancer,aes(x=Age,y=Pregnancies))+geom_boxplot(aes(fill=Outcome))+facet_wrap(Outcome~.)
```








#What is the frequency and relative frequency distribution of diabatic and non-diabetic categories?

```{r}
cat_class <- table(newcancer$Outcome)
cat_class
```

```{r}
rel_freq=cat_class/sample_size
rel_freq
```

#Find the range of patients Age participated in the survey.

```{r}
Age=newcancer$Age
Age_range = range(Age) 
Age_range
```

#We find the correlations



```{r}
par(mar=c(2,2,2,2))
ggplot(newcancer,aes(x=Glucose,y=BMI))+geom_point()+geom_smooth(method='lm',se=FALSE)
```

```{r}
cor(newcancer$Glucose,newcancer$BMI)
```

```{r}
par(mar=c(2,2,2,2))
ggplot(newcancer,aes(x=Insulin,y=BMI))+geom_point()+geom_smooth(method='lm',se=FALSE)
```




```{r}
cor(newcancer$Insulin,newcancer$BMI)
```

```{r}
par(mar=c(2,2,2,2))
ggplot(newcancer,aes(x=BloodPressure,y=BMI))+geom_point()+geom_smooth(method='lm',se=FALSE)
```

```{r}
cor(newcancer$BloodPressure,newcancer$BMI)
```




```{r}
library(caret)
```
```{r}
train_samples <- newcancer$BMI %>%
  createDataPartition(p=0.8,list=FALSE)
head(train_samples)
```


```{r}
model <- lm(BMI~Glucose,data=newcancer)
#model <- lm(sales~.,data=marketing)
model
```

```{r}
model <- lm(BMI~Insulin,data=newcancer)
#model <- lm(sales~.,data=marketing)
model
```


```{r}
model <- lm(BMI~BloodPressure,data=newcancer)
#model <- lm(sales~.,data=marketing)
model
```
```{r}
#split the data into training and test data set
library(dplyr)

```

```{r}
train_samples <- newcancer$BMI %>%
  createDataPartition(p=0.8,list=FALSE)
head(train_samples)
```


```{r}
train <- newcancer[train_samples,]
test <- newcancer[-train_samples,]
model <- lm(BMI~.,data=newcancer)
summary(model)
```


```{r}
pred <- model %>%
  predict(train)
head(pred)
```
##Model performance

```{r}
RMSE <- RMSE(pred,df$BMI)
RMSE
```

```{r}
R2 <- R2(pred,df$BMI)
R2
```

#RSE ERROR

```{r}
sigma(model)   #RSE/mean(marketing$sales)
```

```{r}
sigma(model)*100/mean(newcancer$BMI)  #percentage error
```
